Implementing Option Pricing Model

### 2019-12-21 draft.Rmd
Update draft.Rmd

$$
C(S, K, \sigma,r, T, \delta) = S e^{-\delta T} N(d_{1}) - K e^{-r T} N(d_{2})
$$
$$
\begin{align}
d_{1} &= \frac{\ln{(S/K)} + (r - \delta + \frac{1}{2} \sigma^{2}) T}{\sigma \sqrt{T}} \\
d_{2} &= d_{1} - \sigma \sqrt{T}
\end{align}
$$

@@

$$
\begin{align}
\mbox{Call Delta} &= \frac{\partial C(S, K, \sigma, r, T - t, \delta)}{\partial S} = e^{-\delta (T - t)} N(d_{1}) 
\end{align}
$$

@@

$$
\begin{align}
\mbox{Call Gamma} &=  \frac{\partial^{2} C(S, K, \sigma, r, T - t, \delta)}{\partial S^{2}} = \frac{e^{-\delta (T - t)} N^{\prime}(d_{1})}{S \sigma \sqrt{T - t}} 
\end{align}
$$

@@

![This is the call payoff from Monte Carlo simulation, used 252 time steps, and 100 simulation.](images/Naive.PNG)

![This is the call payoff from Delta-Hedged Monte Carlo simulation, used 252 time steps, and 100 simulation.](images/DeltaHedging.PNG)

![This is the call payoff from Delta-Hedged Monte Carlo simulation, used 252 time steps, and 100 simulation.](images/DeltaGammaHedging.PNG)

@@

From the first "for loop" in the code above, we calculate the Delta for each time step from the Black-Scholes Delta formula. Delta will rebalance discretely for each step for every simulation. We will get a "M*N" matrix for the Delta. And then using the Delta to get the value of control variates. The authors choose the beta1 = -1 which is the appropriate value for this example where they have the exact Delta. The variable "erddt" allow us to compute $E[S_{t_{i+1}}]$ efficiently.

@@

![This is the call payoff from Jump world with Delta-hedging, used 252 time steps, and 100 simulations.](images/DeltaHedgingJump.PNG)

![This is the call payoff from Jump world with Delta-Gamma-hedging, used 252 time steps, and 100 simulations.](images/DeltaGammaHedgingJump.PNG)

>>>>

$$
C(S, K, \sigma, r, T, \delta) = S e^{-\delta T} N(d_{1}) - K e^{-r T} N(d_{2})
$$
$$
d_{1} = \frac{\ln{(S/K)} + (r - \delta + \frac{1}{2} \sigma^{2}) T}{\sigma \sqrt{T}} 
$$
$$
d_{2} = d_{1} - \sigma \sqrt{T}
$$

@@

$$
Call Delta= \frac{\partial C(S, K, \sigma, r, T - t, \delta)}{\partial S} = e^{-\delta (T - t)} N(d_{1}) 
$$

@@

$$
Call Gamma=  \frac{\partial^{2} C(S, K, \sigma, r, T - t, \delta)}{\partial S^{2}} = \frac{e^{-\delta (T - t)} N^{\prime}(d_{1})}{S \sigma \sqrt{T - t}} 
$$

@@

![This is the call payoff from Monte Carlo simulation, used 252 time steps, and 100 simulations.](images/Naive.PNG)

![This is the call payoff from Delta Hedged Monte Carlo simulation, used 252 time steps, and 100 simulations.](images/DeltaHedging.PNG)

![This is the call payoff from Delta-Gamma Hedged Monte Carlo simulation, used 252 time steps, and 100 simulations.](images/DeltaGammaHedging.PNG)

@@

From the first "for loop" in the code above, we calculate the Delta for each time step from the Black-Scholes Delta formula. Delta will rebalance discretely for each step for every simulation. We will get the Delta for each time step. And then using the Delta to get the value of control variates. The authors choose the beta1 = -1 which is the appropriate value for this example where they have the exact Delta. The variable "erddt" allow us to compute $E[S_{t_{i+1}}]$ efficiently.

@@

![This is the call payoff from Jump world with Delta Hedged, used 252 time steps, and 100 simulations.](images/DeltaHedgingJump.PNG)

![This is the call payoff from Jump world with Delta-Gamma Hedged, used 252 time steps, and 100 simulations.](images/DeltaGammaHedgingJump.PNG)
